Computable Poincar\'e--Friedrichs constants\\ for the $L^{p}$ de Rham complex over domains\\ with shellable triangulations

### 2024-08-29 main.tex
clean up

    \item
    Let $F \in \Faces(T)$ and let $z_F \in F$ be its barycenter. 
    Since $\calT$ is finite, we let $\mathring B_F$ be an open neighborhood around $z_F$ so small that it only intersects those $n$-simplices of $\calT$ that already contain $z_F$ and no faces other than $F$.
    Suppose there are distinct $n$-simplices $T_1, T_2, \dots, T_K$ that contain $z_F$. 
    The intersection of any two of them is $F$, and their interiors are disjoint.

    Consider the case that $z_F$ lies on the boundary of $\calM$. 
    If $F$ is contained in at least two distinct $n$-simplices of $\calT$,
    then we can construct an embedded $n$-dimensional open ball that contains $z_F$.
    But that contradicts $z_F$ being on the boundary. 
    So any boundary face can only be contained in one single $n$-simplex.

    If $z_F$ is an interior point of $\calM$, 
    then we can assume that $\mathring B_F$ is homeomorphic to an open $n$-ball and $\partial \mathring B_F$ is homeomorphic to a sphere of dimension $n-1$. 
    At the same time, $X = F \cap \partial \mathring B_F$ is empty if $n=1$ or homeomorphic to a sphere of dimension $n-2$. % TODO: proofread
    We see that $\partial \mathring B_F \setminus X$ has $K$ distinct connected components. 
    But by the auxiliary result above, $K = 2$. 
    We conclude that $F$ is contained in two $n$-simplices of $\calT$.
%     But by construction $\partial \mathring B_F \setminus X$ is homeomorphic to $S \setminus S'$,
%     which has exactly two distinct connected components according to the Jordan-Brouwer separation theorem.
%     If an inner face $F$ were contained in only one $n$-simplex,
%     then we could construct a homeomorphism from the $n$-ball onto itself that maps an interior point on the its boundary, which cannot be.
%     So each inner face is contained in exactly two $n$-simplices. 
%     \todo{More details}

%     If $F$ is contained in only one $n$-simplex, then it must be a face in the boundary of $\calM$. 
%     If $F$ were contained in at least two $n$-simplices,
%     then we could construct a homeomorphism from the $n$-ball onto itself that maps an interior point on the its boundary, which cannot be.
%     So each face within $\partial \calM$ is contained in exactly one $n$-simplex. 
%     \todo{More details}
%     {\color{blue}
%     The doubling $M_{D}$ of the manifold $M$ is obtained by gluing $M$ to a copy of itself along the boundary.
%     The triangulation $\calT$ can be doubled to get a triangulation of the doubled manifold.
%     Any boundary face is an interior face of the doubled manifold two $n$-simplices of the doubled triangulation.
%     So each face within $\partial \calM$ is contained in exactly one $n$-simplex of $\calT$. 
%     }

@@

    So it remains to study the topology of vertex stars. Suppose that $S = \{z\}$ is a singleton simplex. 
    For $\delta > 0$ small enough, 
    \begin{align*}
        B_{\delta}(z) = \left\{ x \in \calM \suchthat d(x,z) \leq \delta \right\},
        \quad 
        S_{\delta}(z) = \left\{ x \in \calM \suchthat d(x,z) = \delta \right\},
    \end{align*}
    are subsets of $\patch_{\calT}(S)$.
    For each $K \in \patch_{\calT}(S)$ that contains $S$ and which has the complementary simplex $F_S$, 
    we easily find homeomorphisms $\phi_{K} : B_{\delta}(z) \cap K \rightarrow K$
    such that 
    $\phi_{K|S}$ is the identity,
    such that 
    $\phi_{K}(S_F) = S_{\delta}(z)$,
    and such that 
    for all $K, K' \in \calT$ with $K' \subseteq K$ we have $\phi_{K|K'} = \phi_{K'}$.

@@

    If $z$ is a boundary vertex of $\calS'$,
    which is the case if and only if $S$ is a boundary simplex, 
    then the underlying space of $\carapace(S)$ is homeomorphic to $S_{\delta}(z)$, 
    which is a topological ball of dimension $n-1$. % TODO: explain why

    \item 
    We show that each vertex star is strongly connected via a short induction argument.
    Clearly, any simplicial $1$-ball and simplicial $1$-sphere is strongly connected. 
    Now, if $n \geq 1$, then any vertex star in an $(n+1)$-dimensional manifold triangulation is strongly connected if all simplicial $n$-balls and $n$-spheres are strongly connected.
    The induction argument implies that each vertex star in $\calT$ is strongly connected.

    \item 
    If the underlying space is connected, then we easily see that the union of the $1$-simplices is path-connected.
    Given $n$-simplices $S,S' \in \calT$, 
    we can thus choose a sequence of $\hat S_0=S,\hat S_1,\dots,\hat S_m=S' \in \calT$ such that $\hat S_{i} \cap \hat S_{i-1} \neq \emptyset$ for all $1 \leq i \leq m$.
    We also notice that each vertex star is strongly connected. 
    We can thus change the first sequence to another $S_0=S,S_1,\dots,S'=S_m \in \calT$ 
    such that $S_{i} \cap S_{i-1}$ is a face of both $S_{i}$ and $S_{i-1}$ for all $1 \leq i \leq m$.
    \end{enumerate}
    All relevant results are proven. 
\end{proof}

@@

    %\todo{Double check this proof and make it more explicit.}
    Write $M = |\calT|$. 
    There is nothing to show if $\calT$ contains only one triangle. 
    We call a triangle $T \in \calT$ \emph{good in $\calT$} if it intersects the boundary $\partial M$ in a non-empty union of edges. 
    Hence a triangle is good in $\calT$ if its intersection with $\partial M$ is either one, two, or three edges,
    and a triangle is not good in $\calT$ if that intersection is either empty only some of its vertices, or a vertex and the opposite edge.
    % TODO: I understand what it means from the rest of the proof, but I believe it could a bit more explicit.
    We show by an induction argument over the number of triangles that every triangulation of a $2$-disk that contains at least two triangles also contains at least two good triangles.

    Clearly, this is the case if the triangulation of the $2$-disk contains two triangles. 
    Now suppose the induction claim is true when the triangulation includes at most $N$ triangles,
    and assume that $\calT$ includes $N+1$ triangles. 
    There are at least two triangles with an edge on the boundary. 
    Suppose that $\calT$ does not have at least two triangles that are good in $\calT$,
    then there exists a triangle $T'$ that intersects $\partial M$ 
    in one edge and its opposite vertex.
    Removing $T'$ splits the manifold into two strongly connected components, each of which is a topological $2$-disk.
    By the induction assumption, each of those components contains at least two triangles 
    that are good in the respective component. 
    So each component has at least one triangle that is good in $\calT$.

    % There exists a triangle $T' \in \calT$ with at least one edge in the boundary. 
    % If $T'$ is good, then we are already done. 
    % Otherwise, $T'$ intersects the boundary at one edge and its opposing vertex.
    % \todo{MV:But what if this is the neighbor of $T'$ and adding $T'$ back makes the triangle bad?}

    Since $\calT$ triangulates a $2$-disk,
    it contains a good triangle $T$. 
    If $T$ has three edges in the boundary, then $T = M$ and we are trivially done. 
    If $T$ intersects with the boundary in exactly one or two edges, 
    then $\overline{M \setminus T}$ is still a topological $2$-disk.
    The triangulation $\calT'$ that is obtained by removing $T$
    is a triangulation of some $2$-disk that intersects $T$ only at either two or one edges.
    Any shelling of $\calT'$ can be extended to a shelling of $\calT$.
%     Let $\calT$ be a simplicial $2$-disk. 
%     If $\calT$ contains only one triangle, then there is nothing to show. 
%     Otherwise, there exists at least one triangle $T$ that touches the boundary of the disk at either one or two edges 
%     {\color{red}Needs proof}. 
%   
%     Now let $\calS$ be any simplicial $2$-sphere. 
%     By removing any triangle $S \in \calS$, we obtain a simplicial $2$-disk, which is shellable. 
%     Any of its shellings can be extended to a shelling of $\calS$ by re-inserting the first triangle $S$.
\end{proof}

@@

\begin{lemma}\label{lemma:existenceofstar}
    Suppose that an $n$-dimensional manifold triangulation $\calT$ has a shelling $T_{0}, T_{1}, T_{2}, \dots, T_{M}$.
    For $0 \leq m < M$, write 
    $$
        X_{m} := T_{0} \cup T_{1} \cup \dots \cup T_{m},
        \qquad 
        I_{m} := X_{m} \cap T_{m+1}.
    $$ 
    Whenever $I_{m}$ is the union of $k$ different facets of $T$, 
    then the intersection of those facets is a simplex $S \in \calT$ of dimension $n-k$ that satisfies 
    $$
        \patch_{X_{m+1}}(S) = \patch_{\calT}(S).
    $$
\end{lemma}
\begin{proof}
    We know $I_{m}$ is a submanifold of the boundary of $T$, and so it must be a collection of $k$ facets
    that constitute the local patch around some simplex $S$ of dimension $n-k$.
    To show that $\patch_{X_{m+1}}(S) = \patch_{\calT}(S)$, let us assume that $T \in \patch_{\calT}(S) \setminus \patch_{X_{m+1}}(S)$.
    By assumption, $S$ must be a boundary simplex of $X_{m+1}$. 
    \todo{Complete this here. The barycenter is contained in the interior of a boundary disk.}
\end{proof}

@@

        \item 
        % \todo{Reflect onto complement and estimate bi-Lipschitz constant}
        We introduce a new mapping $\Theta : |\calR| \rightarrow |\calR^c|$.
        Let $K \in \calR$ be an $n$-simplex and $K' \in \calR^{c}$ be constructed from $K$.
        We let $A_{K} : \Delta^{n} \rightarrow K$ and $A_{K'} : \Delta^{n} \rightarrow K'$
        be affine reference transformations
        that agree on the vertices common to $K$ and $K'$.
        We then define 
        \begin{align*}
            \Theta_{|K} := A_{K'} \circ A_{K}^{-1}.
        \end{align*}
        Notice that $A_{K'}$ and $A_{K}$ have the same singular values. Thus
        \begin{align*}
            \| \Jacobian \Theta_{|K}      \| &\leq \| A_{K'} \| \cdot \| A_{K}^{-1} \| \leq \kappa(A_{K}),
            \\
            \| \Jacobian \Theta_{|K}^{-1} \| &\leq \| A_{K'}^{-1} \| \cdot \| A_{K} \| \leq \kappa(A_{K}).
        \end{align*}

@@

    We define $w'_{m} :=  \Xi_{m}^{\ast} w_{m-1} \in W^{p}\Alt^{k}(T_{m})$,
    where $\Xi_{m} : T_{m} \rightarrow U_{m-1}$ is the reflection mapping
    as in Theorem~\ref{theorem:starreflection}. 
    By construction, $w'_{m} \in W^{p}\Alt^{k}(T_{m})$ with 
    \begin{align*}
        \trace_F w_{m-1} = \trace_F w'_{m}
        . % TODO: notation, 
    \end{align*}
    There exists $w''_{m} \in W^{p}\Alt^{k}(T_{m})$ satisfying 
    \begin{align*}
        \cartan w''_{m} = \cartan u - \cartan w'_{m}, 
        \quad 
        \trace_{\Gamma_{m}} w''_{m} = 0.
    \end{align*}
    Indeed, such $w''_{m}$ exists because 
    \begin{align*}
        \trace_{\Gamma_{m}}( \cartan u - \cartan w'_{m} ) 
        &= 
        \trace_{\Gamma_{m}} \cartan u - \trace_{\Gamma_{m}} \cartan w'_{m}
        \\&= 
        \cartan \trace_{\Gamma_{m}} u - \cartan \trace_{\Gamma_{m}} w'_{m}
        = 
        \cartan \trace_{\Gamma_{m}} u - \cartan \trace_{\Gamma_{m}} w_{m-1}
        = 
        0
        .
    \end{align*}
    Setting $w_{m} := w_{m-1}$ over $\Omega_{m-1}$ and $w_{m} := w'_{m} + w''_{m}$ over $T_{m}$, 
    we find 
    \begin{gather*}
        \cartan w_{m} = \cartan w'_{m} + \cartan w''_{m} = \cartan w'_{m} + \cartan u - \cartan w'_{m} = \cartan u,
        \\
        \trace_{\Gamma_{m}} w_{m} = \trace_{\Gamma_{m}} w'_{m} = \trace_{\Gamma_{m}} w_{m-1}.
    \end{gather*}
    That means that $w_{m} \in W^{p}\Alt^{k}(\Omega_{m})$ with $\cartan w_{m} = \cartan u$ over $\Omega_{m}$.

>>>>

    \todo{Decide which paragraph remains...}

    \item
    Let $F \in \Faces(T)$ and let $z_F \in F$ be its barycenter. 
    Since $\calT$ is finite, we let $\mathring B_F$ be an open neighborhood around $z_F$ so small that it only intersects those $n$-simplices of $\calT$ that already contain $z_F$ and no faces other than $F$.
    Suppose there are distinct $n$-simplices $T_1, T_2, \dots, T_K$ that contain $z_F$. 
    The intersection of any two of them is $F$, but their interiors are disjoint because otherwise they would coincide.

    If $z_F$ is an interior point of $\calM$, 
    then we can assume that $\mathring B_F$ is homeomorphic to an open $n$-ball and $\partial \mathring B_F$ is homeomorphic to a sphere of dimension $n-1$. 
    Consider $X = F \cap \partial \mathring B_F$.
    If $n=1$, then $X$ is empty and $\partial \mathring B_F$ has $K$ distinct connected components. .
    If $n > 1$, then $X$ is homeomorphic to a sphere of dimension $n-2$
    and again $\partial \mathring B_F \setminus X$ has $K$ distinct connected components. 
    But by the auxiliary result above, $K = 2$. 
    We conclude that $F$ is contained in two $n$-simplices of $\calT$.

    Consider the case that $z_F$ lies on the boundary of $\calM$
    and suppose that $F$ is contained in $K$ distinct $n$-simplices of $\calT$.
    By adding at least one dimension, we can double the manifold $\calM$ along the boundary and obtain the doubled manifold $\calM'$. Similarly, we can construct a doubling of the triangulation $\calT'$ such that $F$ is contained in exactly $2K$ distinct $n$-simplices of $\calT'$. We know that $\calM'$ is a manifold without boundary, and hence $F$ is an interior simplex of $\calT'$.
    This implies $K=1$.
    So any boundary face can only be contained in one single $n$-simplex.

@@

    \item 
    So it remains to study the topology of vertex stars. Suppose that $S = \{z\}$ is a singleton simplex. 
    For $\delta > 0$ small enough, 
    \begin{align*}
        B_{\delta}(z) = \left\{ x \in \calM \suchthat d(x,z) \leq \delta \right\},
        \quad 
        S_{\delta}(z) = \left\{ x \in \calM \suchthat d(x,z) = \delta \right\},
    \end{align*}
    are compactly contained subsets of $|\patch_{\calT}(S)|$.
    For each simplex $K \in \patch_{\calT}(S)$ that contains the vertex $z$ and which has the opposite face $F_K$, 
    we easily find homeomorphisms $\phi_{K} : B_{\delta}(z) \cap K \rightarrow K$
    such that 
    $\phi_{K}(z) = z$, 
    such that 
    $\phi_{K}( K \cap S_{\delta}(z) ) = F_{K}$,
    such that 
    for all $K, K' \in \calT$ with $K' \subseteq K$ we have $\phi_{K|K'} = \phi_{K'}$,
    and such that 
    $\phi_{K}$ maps $[0,1]\cdot v$ linearly into $\bbR \cdot v$. 
    This is defines a homeomorphism $\phi : B_{\delta}(z) \rightarrow |\patch_{\calT}(S)|$.

@@

    If $z$ is a boundary vertex of $\calS'$,
    which is the case if and only if $S$ is a boundary simplex, 
    then the underlying space of $\carapace(S)$ is homeomorphic to $S_{\delta}(z) \cap |\patch_{\calT}(S)|$ along $\phi$.
    The vertex star around $z$ within the boundary triangulation $\partial\calT$ is homeomorphic to the ball of dimension $n-1$,
    and it is homeomorphic to $\overline{ B_{\delta}(z) } \cap |\partial\patch_{\calT}(S)|$ along $\phi$. Notice that 
    \begin{align*}
        \partial\left( { B_{\delta}(z) } \cap |\partial\patch_{\calT}(S)| \right)
        =
        S_{\delta}(z) \cap |\patch_{\calT}(S)|
        \cup 
        \overline{ B_{\delta}(z) } \cap |\partial\patch_{\calT}(S)|
        .
    \end{align*}
    Provided that $\delta > 0$ is small enough, there exists a homeomorphism $\phi'$ from $\overline{B_{\delta}(z)} \cap |\calT|$
    onto the closed unit ball. Necessarily, this homeomorphism maps the boundary of $\overline{B_{\delta}(z)} \cap |\calT|$, which contains $z$, onto the unit sphere. Since the image of $\overline{ B_{\delta}(z) } \cap |\partial\patch_{\calT}(S)|$ along $\phi'$ is still homeomorphic to a disk of dimension $n-1$, so must be the image of $S_{\delta}(z) \cap |\patch_{\calT}(S)|$ under $\phi'$.
    But that just means that $\carapace(S)$ triangulates a topological ball of dimension $n-1$.

    \item 
    We show that each vertex star is strongly connected via a short induction argument.
    Clearly, any simplicial $1$-ball and simplicial $1$-sphere are strongly connected. 
    Now, if $n \geq 1$, then any vertex star in any $(n+1)$-dimensional manifold triangulation is already strongly connected if all simplicial $n$-balls and $n$-spheres are strongly connected.
    The induction argument implies that each vertex star in $\calT$ is strongly connected.

    \item 
    If the underlying space is connected, then we easily see that the union of the $1$-simplices is path-connected.
    Given $n$-simplices $S,S' \in \calT$, 
    we can thus choose a sequence of $\hat S_0=S,\hat S_1,\dots,\hat S_m=S' \in \calT$ such that $\hat S_{i} \cap \hat S_{i-1} \neq \emptyset$ for all $1 \leq i \leq m$, and so each two consecutive simplices in that sequence have at least one vertex in common. 
    As each vertex star is strongly connected, 
    we can thus assume without loss of generality that the sequence $S_0=S,S_1,\dots,S'=S_m \in \calT$ 
    is such that $S_{i} \cap S_{i-1}$ is a face of both $S_{i}$ and $S_{i-1}$ for all $1 \leq i \leq m$.
    This just means that $\calT$ is strongly connected. 
    \end{enumerate}
    All relevant results are proven. 
\end{proof}

@@

    Write $M = |\calT|$. 
    There is nothing to show if $\calT$ contains only one triangle. 
    We call a triangle $T \in \calT$ \emph{good in $\calT$} if it intersects the boundary $\partial M$ in a non-empty union of edges. 
    Hence a triangle is good in $\calT$ if its intersection with $\partial M$ is either one, two, or three edges,
    and a triangle is not good in $\calT$ if that intersection is either empty, only some of its vertices, or a vertex and the opposite edge.
    % DONE: I understand what it means from the rest of the proof, but I believe it could a bit more explicit.
    We show by an induction argument over the number of triangles that every triangulation of a $2$-disk that contains at least two triangles also contains at least two good triangles.

    Clearly, this is the case if the triangulation of the $2$-disk contains two triangles. 
    Now suppose the induction claim is true when the triangulation includes at most $N$ triangles,
    and assume that $\calT$ includes $N+1$ triangles. 
    There are at least two triangles with an edge on the boundary. 
    Suppose that $\calT$ does not have at least two triangles that are good in $\calT$,
    then there exists a triangle $T'$ that intersects $\partial M$ 
    in one edge and its opposite vertex.
    Removing $T'$ splits the manifold into two strongly connected components, each of which is a topological $2$-disk.
    By the induction assumption, each of those components contains at least two triangles 
    that are good in the respective component. 
    So each component has at least one triangle that is good in $\calT$. 
    Hence $\calT$ contains two good triangles, which completes the induction step.

    We conclude that whenever $\calT$ triangulates a $2$-disk,
    it contains a good triangle $T$. 
    If $T$ has three edges in the boundary, then $T = M$ and we are trivially done. 
    If $T$ intersects with the boundary in exactly one or two edges, 
    then $\overline{M \setminus T}$ is still a topological $2$-disk.
    The triangulation $\calT'$ that is obtained by removing $T$
    is a triangulation of some $2$-disk that intersects $T$ only at either two or one edges.
    Any shelling of $\calT'$ can be extended to a shelling of $\calT$.
    The proof is complete. 
\end{proof}

@@

\begin{lemma}\label{lemma:existenceofstar}
    Suppose that an $n$-dimensional manifold triangulation $\calT$ has a shelling $T_{0}, T_{1}, T_{2}, \dots, T_{M}$.
    For $0 \leq m < M$, write 
    $$
        X_{m} := T_{0} \cup T_{1} \cup \dots \cup T_{m},
        \qquad 
        I_{m} := X_{m} \cap T_{m+1}.
    $$ 
    Whenever $I_{m}$ is the union of $k$ different facets of $T$, 
    then the intersection of those facets is an interior simplex $S \in \calT$ of dimension $n-k$ that satisfies 
    $$
        \patch_{X_{m+1}}(S) = \patch_{\calT}(S).
    $$
\end{lemma}
\begin{proof}
    We know $I_{m}$ is a submanifold of the boundary of $T$, and so it must be a collection of $k$ facets
    that constitute the local patch around some simplex $S$ of dimension $n-k$.
    By assumption, $S$ must be a boundary simplex of $X_{m}$ and it is an interior simplex of $X_{m+1}$. 
    But then $S$ cannot be a subsimplex of any of the simplices $T_{m+1}, \dots, T_{M}$,
    which means that $\patch_{X_{m+1}}(S) = \patch_{\calT}(S)$. 
    This had to be shown.
\end{proof}

@@

        \item 
        We introduce a new mapping $\Theta : |\calR| \rightarrow |\calR^c|$.
        Let $K \in \calR$ be an $n$-simplex and $K' \in \calR^{c}$ be constructed from $K$.
        We let $A_{K} : \Delta^{n} \rightarrow K$ and $A_{K'} : \Delta^{n} \rightarrow K'$
        be affine reference transformations
        that agree on the vertices common to $K$ and $K'$.
        We then define 
        \begin{align*}
            \Theta_{|K} := A_{K'} \circ A_{K}^{-1}.
        \end{align*}
        Notice that $A_{K'}$ and $A_{K}$ have the same singular values. Thus
        \begin{align*}
            \| \Jacobian \Theta_{|K}      \| &\leq \| A_{K'} \| \cdot \| A_{K}^{-1} \| \leq \kappa(A_{K}),
            \\
            \| \Jacobian \Theta_{|K}^{-1} \| &\leq \| A_{K'}^{-1} \| \cdot \| A_{K} \| \leq \kappa(A_{K}).
        \end{align*}

@@

    We define $w'_{m} :=  \Xi_{m}^{\ast} w_{m-1} \in W^{p}\Alt^{k}(T_{m})$,
    where $\Xi_{m} : T_{m} \rightarrow U_{m-1}$ is the reflection mapping
    as in Theorem~\ref{theorem:starreflection}. 
    By construction, $w'_{m} \in W^{p}\Alt^{k}(T_{m})$ with 
    \begin{align*}
        \trace_F w_{m-1} = \trace_F w'_{m}
        . 
    \end{align*}
    There exists $w''_{m} \in W^{p}\Alt^{k}(T_{m})$ satisfying 
    \begin{align*}
        \cartan w''_{m} = \cartan u - \cartan w'_{m}, 
        \quad 
        \trace_{\Gamma_{m}} w''_{m} = 0.
    \end{align*}
    Indeed, such $w''_{m}$ exists because 
    \begin{align*}
        \trace_{\Gamma_{m}}( \cartan u - \cartan w'_{m} ) 
        &= 
        \trace_{\Gamma_{m}} \cartan u - \trace_{\Gamma_{m}} \cartan w'_{m}
        \\&= 
        \cartan \trace_{\Gamma_{m}} u - \cartan \trace_{\Gamma_{m}} w'_{m}
        = 
        \cartan \trace_{\Gamma_{m}} u - \cartan \trace_{\Gamma_{m}} w_{m-1}
        = 
        0
        .
    \end{align*}
    Setting $w_{m} := w_{m-1}$ over $\Omega_{m-1}$ and $w_{m} := w'_{m} + w''_{m}$ over $T_{m}$, 
    we find 
    \begin{gather*}
        \cartan w_{m} = \cartan w'_{m} + \cartan w''_{m} = \cartan w'_{m} + \cartan u - \cartan w'_{m} = \cartan u,
        \\
        \trace_{\Gamma_{m}} w_{m} = \trace_{\Gamma_{m}} w'_{m} = \trace_{\Gamma_{m}} w_{m-1}.
    \end{gather*}
    That means that $w_{m} \in W^{p}\Alt^{k}(\Omega_{m})$ with $\cartan w_{m} = \cartan u$ over $\Omega_{m}$.
